Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature Values

### 2022-04-25 doc/manuscript.tex
.

Çalışma kapsamında geliştirilen tüm çözümleme programları ve üretilen veriler bir Github kod deposunda açık kaynak halde 
sunulmuştur\cite{ccct2022github}. Rationales behind all the selections in the analysis were explained in further sections.

>>>>

Çalışma kapsamında geliştirilen tüm çözümleme programları ve üretilen veriler bir Github kod deposunda açık kaynak halde
sunulmuştur\cite{Oktas_Code_CCT_2022}. Rationales behind all the selections in the analysis were explained in further
sections.
